### 2007-01-12 Documentation/Paper2/paper2.tex
*** empty log message ***

@@

How defined, what good for (physics examples: AstroNus, Schwetz priors, atm. neutrinos, octant degeneracy,
).

Eg. Damping, Hamiltonian, MAVANS, Toshi etc.

\section{Simulation of new experiment features and \AEDL\ changes}

>>>>

The probability calculation in \GLOBES\ 
Eg. Damping, Hamiltonian, MAVANS, Toshi etc.

@@

In order to include correlations and degeneracies, \GLOBES\ provides
(local) maginalization routines to project the fit manifold onto
a subspace. For example, if one wants to compute the $\stheta$ precision,
one scans the $\stheta$ direction and marginalizes for each fixed $\stheta$
over the other oscillation parameters. This marginalization is performed
after the systematics $\chi^2_{\mathrm{pull}}$ in \equ{chipull} (or similar) 
has been determined:
\begin{equation}
 \chi^2_{\mathrm{proj}}(\boldsymbol{\lambda_1}) := \min_{\{ \boldsymbol{\lambda_2} \} } \left( \, \chi^2_{\mathrm{pull}} (\boldsymbol{\lambda_1} , \boldsymbol{\lambda_2} ) \, \right) \, .
\label{equ:margin}
\end{equation}
In this case, the parameter space of oscillation parameters 
$\boldsymbol{\lambda}$ is projected onto the subspace $\boldsymbol{\lambda_1}$.
If one wants to include external input which only depends on the oscillation
parameters and not on systematics, one can do this at this level. \GLOBES\ provides
the pre-defined possibility to include external Gaussian constraints on the 
oscillation parameters (and the matter density, which is treated as another
oscillation parameter). For example, an external constraint on $\theta_{12}$
is added before the marginalition in \equ{margin} by the replacement after the
systematics minimization
\begin{equation}
 \chi^2_{\mathrm{pull}}(\boldsymbol{\lambda}) \rightarrow \chi^2_{\mathrm{pull}}(\boldsymbol{\lambda})  +
 \frac{(\theta_{12} - \theta_{12}^0)^2}{\sigma_{\theta_{12}}^2}
\label{equ:priors}
\end{equation}
with the central value $\theta_{12}^0$, where the input is added, and
the $1\sigma$ Gaussian error $\sigma_{\theta_{12}}$. This corresponds to an external
measurement of the solar mixing angle at the best-fit value $\theta_{12}^0$
with the error $\sigma_{\theta_{12}}$.

In practice, the external error on $\theta_{12}$ may not be Gaussian or one may
want to add other external information. Therefore,
\GLOBESN\ and higher provides the concept of user-defined priors  $f(\boldsymbol{\lambda})$. 
Instead of \equ{priors}, we then have
\begin{equation}
 \chi^2_{\mathrm{pull}}(\boldsymbol{\lambda}) \rightarrow \chi^2_{\mathrm{pull}}(\boldsymbol{\lambda})  + f(\boldsymbol{\lambda}) \, .
\label{equ:userpriors}
\end{equation}
One can easily imagine that this simple concept allows for a high degree of freedom. Examples where
this feature has been used as an experimental feature are the combination of terrestrial neutrino
data with the information from neutrino telescopes~\cite{Winter:2006ce} and the combination of long-baseline data with atmospheric neutrino data~\cite{Huber:2005ep,Campagne:2006yx} (CORRECT?).
Another very interesting option is the use of penalties in degeneracy localization, as suggested by Thomas
Schwetz. For example, if the minimizer runs into the wrong octant, user-defined priors can be
used to add a penalty and prevent it from doing so.

\section{\AEDL\ changes and new experiment prototypes}
